Untitled

### 2021-03-13 ms/manuscript.Rmd
Update MS

We surveyed filmy ferns on Moorea as part of a larger study including all ferns of Moorea and Tahiti [@Nitta2017].
During this study, `r n_distinct(moorea_sites$site)` sampling sites were established from \circa{ }200 m to 1200 m primarily along trails to the summits of three large peaks on Moorea: Mt. Rotui (899 m), Mt. Mouaputa (880 m), and Mt. Tohiea (1206 m).
At each site, sporophytes were sampled in a single 10 m × 10 m plot, and gametophytes sampled in two to three 50 cm × 50 cm plots located within the sporophyte plot.
To estimate abundance of sporophytes, the 10 m × 10 m plot was subdivided into 25 2 m × 2 m subplots, and the presence of species in the sporophyte phase in each subplot was summed such that each species was assigned an abundance rank from 1 to 25.
For the gametophyte plots, each 50 cm x 50 cm plot was subdivided into 25 5 x 5 cm squares, and a single gametophyte selected closest to the center of each square, to later be identified to species using DNA barcoding (see below).
Epiphytes were sampled to a maximum height of \circa{ }2 m on their host plants.
For additional details on sampling procedure, see @Nitta2017.
The growth habit of each species was scored based on field observations as terrestrial, saxicolous, low elevation epiphyte (mostly occurring outside of cloud forest, \ie, below \circa{ }500 m), or high elevation epiphyte (mostly occurring in cloud forest, \ie, above \circa{ }500 m).

@@

A general correlation of DT with habitat was observed in sporophytes (`r figure("dt")`a).
The two terrestrial species lacked DT, although *C. apiifolia* showed slightly greater ability to recover by 48 h compared to *Abrodictyum dentatum* (Bosch) Ebihara & K. Iwats., which completely failed to recover from even the gentlest treatment of 2 d at --38 NaCl (more stringent tests were not conducted on *A. dentatum* after confirming its lack of DT at this level).
Saxicolous species (*Crepidomanes kurzii* (Bedd.) Tagawa & K. Iwats., *Polyphlebium endlicherianum* (C. Presl) Ebihara & K. Iwats., and *Vandenboschia maxima* (Blume) Copel.) also had low DT; only *C. kurzii* was able to recover from desiccation up to --86 MPa for 2 d but not more.
Nearly all epiphytic species were capable of recovering from desiccation of up to 2 d at --86 MPa.
*Crepidomanes bipunctatum* (Poir.) Copel., a widespread low-elevation epiphyte, showed the greatest ability to recover from desiccation across all treatments.
Interestingly, high-elevation epiphytes *Hymenophyllum multifidum* (G. Forst.) Sw. and *Hymenophyllum polyanthos* (Sw.) Sw. could recover from desiccation at --86 or --282 MPa for 15 d, but not --38 MPa.

>>>>

We surveyed filmy ferns on Moorea as part of a larger study including all ferns of Moorea and Tahiti [@Nitta2017].
During this study, `r n_distinct(moorea_sites$site)` sampling sites were established from \circa{ }200 m to 1200 m primarily along trails to the summits of three large peaks on Moorea: Mt. Rotui (899 m), Mt. Mouaputa (880 m), and Mt. Tohiea (1206 m).
At each site, sporophytes were sampled in a single 10 m × 10 m plot, and gametophytes sampled in two to three 50 cm × 50 cm plots located within the sporophyte plot.
To estimate abundance of sporophytes, the 10 m × 10 m plot was subdivided into 25 2 m × 2 m subplots, and the presence of species in the sporophyte phase in each subplot was summed such that each species was assigned an abundance rank from 1 to 25.
For the gametophyte plots, each 50 cm x 50 cm plot was subdivided into 25 5 x 5 cm squares, and a single gametophyte selected closest to the center of each square, to later be identified to species using DNA barcoding (see below).
Epiphytes were sampled to a maximum height of \circa{ }2 m on their host plants.
For additional details on sampling procedure, see @Nitta2017.
The growth habit of each species was scored based on field observations as terrestrial, saxicolous, low elevation epiphyte (mostly occurring outside of cloud forest, \ie, below \circa{ }500 m), or high elevation epiphyte (mostly occurring in cloud forest, \ie, above \circa{ }500 m).
*Crepidomanes bipunctatum* (Poir.) Copel. and *C. humile* (G. Forst.) Bosch were observed growing as both epiphytes and saxicoles, but were treated as epiphytes to distinguish them from exclusively saxicolous species.

@@

A general correlation of DT with habitat was observed in sporophytes (`r figure("dt")`a).
The two terrestrial species lacked DT, although *C. apiifolia* showed slightly greater ability to recover by 48 h compared to *Abrodictyum dentatum* (Bosch) Ebihara & K. Iwats., which completely failed to recover from even the gentlest treatment of 2 d at --38 NaCl (more stringent tests were not conducted on *A. dentatum* after confirming its lack of DT at this level).
Saxicolous species (*Crepidomanes kurzii* (Bedd.) Tagawa & K. Iwats., *Polyphlebium endlicherianum* (C. Presl) Ebihara & K. Iwats., and *Vandenboschia maxima* (Blume) Copel.) also had low DT; only *C. kurzii* was able to recover from desiccation up to --86 MPa for 2 d but not more.
Nearly all epiphytic species were capable of recovering from desiccation of up to 2 d at --86 MPa.
*Crepidomanes bipunctatum*, a widespread low-elevation epiphyte, showed the greatest ability to recover from desiccation across all treatments.
Interestingly, high-elevation epiphytes *Hymenophyllum multifidum* (G. Forst.) Sw. and *Hymenophyllum polyanthos* (Sw.) Sw. could recover from desiccation at --86 or --282 MPa for 15 d, but not --38 MPa.
